Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design

### 2016-10-06 MSR-design.tex
note about ultimate coupling goal.

The basis for this quick synopsis comes from \cite{wiki:Molten_salt_reactor}. 
Research into \glspl{MSR} began in earnest with the \gls{ARE}, with experiments 
shared between \gls{ORNL} and what is now \gls{INL}. The \gls{ARE} used 
NaF-ZrF$_4$-UF$_4$ (53-41-6 mol\%) as fuel. The reactor was moderated by 
beryllium oxide (BeO), used liquid sodium as the secondary coolant, and had a 
peak temperature around 860 \textdegree C. The \gls{ARE} managed to generate
100 MWh over the course of nine days in 1954. There was another reactor that
went critical at \gls{ORNL} in 1957 called the Pratt and Whitney Aircraft Reactor-1
(PWAR-1). Although it produced essentially no power, the PWAR-1 is still one of
only three critical MSRs ever built.

@@

\begin{enumerate}
\item Test whether \code{gmsh} can generate heterogeneous 3D mesh structure
  like that in the actual \gls{MSRE} geometry.
\item For expected range of temperatures and some defined sequence of
  temperature step sizes, generate table of few-group neutronics cross sections
  with \code{SERPENT}.
  \begin{itemize}
    \item If \code{gmsh}, or that failing \code{cubit}, is capable of generating
      heterogeneous grid, we can generate unique cross regions for each region
    \item If we cannot generate heterogeneous grid, we will have to homogenize
      the cross sections similar to what is done in
      \cite{kophazi_development_2009}.
  \end{itemize}
\item Armed with tables for quick interpolation of cross sections, we should be
  able to perform coupled calculations for neutron density and
  temperature.
  \begin{itemize}
    \item As a first pass, the fuel salt flow velocity can be a user input as
      opposed to a non-linear variable that is a function of temperature.
    \item We will need to decide whether neutron and temperature calculations
      should be performed on the same grid, and in transient calculations
      whether those two fields should be updated on the same step-size.
      \begin{itemize}
        \item If not using the same grid and/or step-size, the neutronic and
          temperature calculations will need to be split into their own
          applications and coupling will have to be performed using the MOOSE
          multi-app system.
      \end{itemize}
  \end{itemize}
\end{enumerate}

>>>>

The basis for this quick synopsis comes from \cite{wikipedia_molten_2016}. 
Research into \glspl{MSR} began in earnest with the \gls{ARE}, with experiments 
shared between \gls{ORNL} and what is now \gls{INL}. The \gls{ARE} used 
NaF-ZrF$_4$-UF$_4$ (53-41-6 mol\%) as fuel. The reactor was moderated by 
beryllium oxide (BeO), used liquid sodium as the secondary coolant, and had a 
peak temperature around 860 \textdegree C. The \gls{ARE} managed to generate
100 MWh over the course of nine days in 1954. There was another reactor that
went critical at \gls{ORNL} in 1957 called the Pratt and Whitney Aircraft Reactor-1
(PWAR-1). Although it produced essentially no power, the PWAR-1 is still one of
only three critical MSRs ever built.

@@

\begin{enumerate}
\item Test whether \code{gmsh} can generate heterogeneous 3D mesh structure
  like that in the actual \gls{MSRE} geometry.
\item For expected range of temperatures and some defined sequence of
  temperature step sizes, generate table of few-group neutronics cross sections
  with \code{SERPENT}.
  \begin{itemize}
    \item If \code{gmsh}, or that failing \code{cubit}, is capable of generating
      heterogeneous grid, we can generate unique cross regions for each region
    \item If we cannot generate heterogeneous grid, we will have to homogenize
      the cross sections similar to what is done in
      \cite{kophazi_development_2009}.
  \end{itemize}
\item Armed with tables for quick interpolation of cross sections, we should be
  able to perform coupled calculations for neutron density and
  temperature.
  \begin{itemize}
    \item As a first pass, the fuel salt flow velocity can be a user input as 
            opposed to a non-linear variable that is a function of temperature.
    \item However, the natural convection impacts on salt flow will 
            significantly contribute to reactor dynamics and the ultimate goal 
            will be to couple neutron flux and flow directly via 
            temperature.
    \item We will need to decide whether neutron and temperature calculations
      should be performed on the same grid, and in transient calculations
      whether those two fields should be updated on the same step-size.
      \begin{itemize}
        \item If not using the same grid and/or step-size, the neutronic and
          temperature calculations will need to be split into their own
          applications and coupling will have to be performed using the MOOSE
          multi-app system.
      \end{itemize}
  \end{itemize}
\end{enumerate}
